Self Regulation Ontology Retest Analyses

### 2018-12-13 code/analysis_nbs/ResponseToReviewers.Rmd

```{r}
rt_ddm_vars = measure_labels %>%
  filter(overall_difference %in% c("non-contrast", "contrast")) %>%
  select(dv)

rt_ddm_vars = rt_ddm_vars[,1]

if(from_gh){
  eval(parse(text = getURL('https://raw.githubusercontent.com/zenkavi/SRO_Retest_Analyses/master/code/helper_functions/make_rel_df.R', ssl.verifypeer = FALSE)))
}else{
  source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/helper_functions/make_rel_df.R')
}
```

```{r}
rel_df = make_rel_df(test_data, retest_data, metrics = c("icc3.k", 'icc2.1'), vars = rt_ddm_vars)

rel_df %>%
  left_join(measure_labels %>% select("rt_acc", "raw_fit", "dv", "overall_difference"), by = "dv") %>%
  mutate(overall_difference = factor(overall_difference, levels = c("non-contrast", "contrast"), labels = c("Non-contrast", "Contrast")),
         raw_fit = factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels = c("Raw", "EZ", "HDDM")),
         rt_acc = factor(rt_acc, levels = c("drift rate", "threshold", "non-decision", "rt", "accuracy"), labels = c("Drift Rate", "Threshold", "Non-decision", "RT", "Accuracy"))) %>%
  ggplot(aes(raw_fit, icc2.1, fill=rt_acc))+
  geom_boxplot()+
  facet_wrap(~overall_difference)+
  geom_hline(yintercept=0, linetype="dashed")+
  guides(fill = guide_legend(nrow=3, byrow=FALSE))+
  theme(legend.title = element_blank())
```

```{r}
rel_df %>%
  left_join(measure_labels %>% select("rt_acc", "raw_fit", "dv", "overall_difference"), by = "dv") %>%
  mutate(overall_difference = factor(overall_difference, levels = c("non-contrast", "contrast"), labels = c("Non-contrast", "Contrast")),
         raw_fit = factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels = c("Raw", "EZ", "HDDM")),
         rt_acc = factor(rt_acc, levels = c("drift rate", "threshold", "non-decision", "rt", "accuracy"), labels = c("Drift Rate", "Threshold", "Non-decision", "RT", "Accuracy"))) %>%
  group_by(overall_difference, raw_fit, rt_acc) %>%
  summarise(mean_icc2.1 = mean(icc2.1),
            tvals_icc2.1 = get_tval(icc2.1))
```

*Response:* We thank the reviewer for providing a potential explanation for the low reliability of the EZ threshold and non-decision time variables for contrasts. In our data the EZ thresholds and non-decision times for contrasts are systematically different than 0 suggesting that they capture a systematic difference instead of the common assumption of noise. Still these contrast measures are much less reliable than non-contrast measures. Similar to the constrasts in raw measures of response times and accuracies, which are less reliable than their non-contrast counterparts, measures do not have to be noise to be unreliable. 
Because the assumption fails we chose not to present this possibility in the manuscript. The details of our analyses on this question can however be found [on:  https://zenkavi.github.io/SRO_Retest_Analyses/output/reports/ResponseToRevisers.nb.html#R1](https://zenkavi.github.io/SRO_Retest_Analyses/output/reports/ResponseToRevisers.nb.html#R1)

@@

##R1.6
>In our paper, we report ICC(2,1)...

TODO: All results with ICC using ICC(2,1) instead of ICC(3,k)  
- [DONE] recode `get_retest_stats` to report all kinds of ICCs
- make new `rel_df` (with both types of ICC for retest paper vars)
- make new `boot_df` (with both types of ICC for retest paper vars)
- rerun MCMC models with ICC(2,1)

```{r}
rel_df = make_rel_df(test_data, retest_data, metrics = c("icc3.k", 'icc2.1', 'pearson'), vars = rt_ddm_vars)

rel_df %>%
  gather(key, value, -dv, -icc2.1)%>%
  ggplot(aes(icc2.1, value))+
  geom_point()+
  facet_wrap(~key)+
  geom_abline(aes(slope=1, intercept=0), linetype="dashed")+
  xlim(-0.5, 1)+
  ylim(-0.5, 1)+
  ylab("")
```

### 2018-12-13 code/analysis_nbs/ResponseToReviewers.Rmd

---
title: 'SRO Retest Response to Reviewers'
output:
github_document:
toc: yes
toc_float: yes
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
from_gh=FALSE
script_loader = function(file, path, remote=from_gh){
  if(remote){
    library(RCurl)
    gh_path = paste('https://raw.githubusercontent.com/zenkavi',
                     strsplit(path, '/')[[1]][1],
                     'master',
                     paste(strsplit(path, '/')[[1]][-1],'/',sep = '', collapse=""),
                    sep="/")
    eval(parse(text = getURL(paste0(gh_path, file), ssl.verifypeer = FALSE)))
  }else{
    source(paste0('/Users/zeynepenkavi/Dropbox/PoldrackLab/',path, file))
  }
}

@@

library(tidyverse)
library(jsonlite)

cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
theme_set(theme_bw())
ggplot <- function(...) ggplot2::ggplot(...) + scale_fill_manual(values=cbbPalette) + scale_color_manual(values=cbbPalette)+theme(legend.position="bottom")

to_keep = c('from_gh',"script_loader", "cbbPalette", "ggplot")
```

@@

##R1.5
>If the common assumption that threshold and non-decision time do not vary between conditions in tasks with intermixed trials is true, we could interpret the contrasts between those parameters generated from the EZ diffusion model to simply be noise. If that were the case, we shouldn't expect those contrasts to be reliable.

TODO: 
### Are EZ threshold and non-decision time contrast estimates are >0?

Yes. The assumption that thresholds and non-decision times are the same across conditions does not hold in our data as the distributions of these parameters are systematically different than 0 for both time point.

```{r}
script_loader(file='ddm_subject_data.R', path='SRO_DDM_Analyses/code/workspace_scripts/')
```

@@

```{r}
retest_data %>%
  select(ez_contrast_vars$dv) %>%
  mutate(time = "Time 1") %>%
  bind_rows(test_data %>%
              select(ez_contrast_vars$dv) %>%
              mutate(time = "Time 2")) %>%
  gather(key, value, -time) %>%
  rename(dv = key) %>%
  left_join(measure_labels %>% select(dv, rt_acc), by = 'dv') %>%
  ggplot(aes(value))+
  geom_density(aes(group=dv, col=rt_acc), linetype="dotted")+
  geom_density(aes(col=rt_acc), size=2.5)+
  xlim(-1.5,1.5)+
  geom_vline(xintercept=0, linetype="dashed", size=1.5)+
  theme(legend.title=element_blank())+
  xlab("")+
  ylab("")+
  facet_wrap(~time)
```

```{r}
retest_data %>%
  select(ez_contrast_vars$dv) %>%
  mutate(time = "Time 1") %>%
  bind_rows(test_data %>%
              select(ez_contrast_vars$dv) %>%
              mutate(time = "Time 2")) %>%
  gather(key, value, -time) %>%
  rename(dv = key) %>%
  left_join(measure_labels %>% select(dv, rt_acc), by = 'dv') %>%
  group_by(rt_acc, time) %>%
  summarise(tvals=get_tval(value),
            means=get_mean(value))
```

### Are their reliabilities >0?

Although the thresholds and non-decision times for contrasts are >0 still have low reliabilities.

@@

```{r}
rt_ddm_vars = measure_labels %>%
  filter(overall_difference %in% c("non-contrast", "contrast")) %>%
  select(dv)

rt_ddm_vars = rt_ddm_vars[,1]

script_loader(file="make_rel_df.R", path="SRO_Retest_Analyses/code/helper_functions/")
```

```{r message=FALSE, warning=FALSE}
rel_df = make_rel_df(test_data, retest_data, metrics = c("icc3.k", 'icc2.1'), vars = rt_ddm_vars)

@@

```{r echo=FALSE}
rm(list=setdiff(ls(), to_keep))
```

##R1.6
>In our paper, we report ICC(2,1)...

TODO: All results with ICC using ICC(2,1) instead of ICC(3,k)  
- [DONE] recode `get_retest_stats` to report all kinds of ICCs
- make new `rel_df` (with both types of ICC for retest paper vars)
- make new `boot_df` (with both types of ICC for retest paper vars)
- rerun MCMC models with ICC(2,1)

```{r message=FALSE}
script_loader(file='subject_data.R', path="SRO_Retest_Analyses/code/workspace_scripts/")

script_loader(file='make_rel_df.R', path="SRO_Retest_Analyses/code/helper_functions/")

script_loader(file='measure_labels_data.R', path="SRO_Retest_Analyses/code/workspace_scripts/")
```

```{r}
rel_df = make_rel_df(test_data, retest_data, metrics = c("icc3.k", 'icc2.1', 'pearson', 'spearman'))
```

```{r}
rel_df %>%
  gather(key, value, -dv, -icc2.1)%>%
  left_join(measure_labels %>% select(dv, task),by="dv") %>%
  ggplot(aes(icc2.1, value))+
  geom_point(aes(col=task))+
  facet_wrap(~key)+
  geom_abline(aes(slope=1, intercept=0), linetype="dashed")+
  xlim(-0.5, 1)+
  ylim(-0.5, 1)+
  ylab("")+
  theme(legend.title = element_blank(),
        aspect.ratio = 1)

measure_labels %>%
  arrange(task)
```

### 2018-12-14 code/analysis_nbs/ResponseToReviewers.Rmd

*Response:* We thank the reviewer for providing a potential explanation for the low reliability of the EZ threshold and non-decision time variables for contrasts. In our data the EZ thresholds and non-decision times for contrasts are systematically different than 0 suggesting that they capture a systematic difference instead of the common assumption of noise. Still these contrast measures are much less reliable than non-contrast measures. Similar to the constrasts in raw measures of response times and accuracies, which are less reliable than their non-contrast counterparts, measures do not have to be noise to be unreliable. 
Because the assumption fails we chose not to present this possibility in the manuscript. The details of our analyses on this question can however be found [on:  https://zenkavi.github.io/SRO_Retest_Analyses/output/reports/ResponseToRevisers.nb.html#R1](https://zenkavi.github.io/SRO_Retest_Analyses/output/reports/ResponseToRevisers.nb.html#R1)

```{r echo=FALSE}
rm(list=setdiff(ls(), to_keep))
```

##R1.6
>In our paper, we report ICC(2,1)...

TODO: All results with ICC using ICC(2,1) instead of ICC(3,k)  
- [DONE] recode `get_retest_stats` to report all kinds of ICCs
- [DONE] make new `rel_df` (with both types of ICC for retest paper vars)
- make new `boot_df` (with both types of ICC for retest paper vars)
- rerun MCMC models with ICC(2,1)

@@

script_loader(file='make_rel_df.R', path="SRO_Retest_Analyses/code/helper_functions/")

script_loader(file='measure_labels_data.R', path="SRO_Retest_Analyses/code/workspace_scripts/")
```

```{r}
rel_df = make_rel_df(test_data, retest_data, metrics = c("icc3.k", 'icc2.1', 'pearson', 'spearman'))
```

```{r message=FALSE}
rel_df %>%
  gather(key, value, -dv, -icc2.1)%>%
  left_join(measure_labels %>% select(dv, task),by="dv") %>%
  ggplot(aes(icc2.1, value))+
  geom_point(aes(col=task))+
  facet_wrap(~key)+
  geom_abline(aes(slope=1, intercept=0), linetype="dashed")+
  xlim(-0.5, 1)+
  ylim(-0.5, 1)+
  ylab("")+
  theme(legend.title = element_blank(),
        aspect.ratio = 1)
```

### 2018-12-17 code/SRO_Retest_Analyses.Rmd
working on response to reviewers

```{r, message=FALSE, warning=FALSE, include=FALSE}
source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/SRO_Retest_Analyses_Workspace.R')
```

>>>>

```{r, message=FALSE, warning=FALSE, include=FALSE}
from_gh = TRUE
source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/workspace_scripts/SRO_Retest_Analyses_Workspace.R')
```
